Think deep for reef resilience

### 2025-08-22 paper/paper_draft.qmd
Add scatter plot that shows the distributions of reef depth and incoming
connectivity. The colour indicates the mean carbonate budget maintenance level across theta0 values.

>>>>

![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming connectivity for each reef. Point colours represent the mean number of years each reef maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
fig-align="center" width="10cm"}
